Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-24 paper.tex
Minor edit

Note that matches represent only those partial applications where arguments are added without gaps.
Hence for a rule $r : A → B → C → D$, the applications $r~a~\_ : B \to D$ and $r~a~b : D$ for some $a : A$ and $b : B$ correspond to matches, but not $r~\_~b : A \to D$.
This prevents us from constructing $r~a~b$ in two different but ultimately redundant ways.
The term orders used in various saturation calculi serve a similar function.

@@

To account for this fact, we partition the set of premises of each rule into maximal subsets of premises connected by shared variables, called \emph{variable clusters}, using the same construction as Aesop's \emph{metavariable clusters}~\cite{Aesop}.
The variable clusters share no variables with each other, so each can be treated as a separate rule with its own rule state.
Finding a complete match for a rule then amounts to finding one complete match for each of its clusters.
The slots within each cluster can be ordered to ensure that each slot shares at least one variable with the previous slots, satisfying our assumption.

>>>>

Note that matches represent only those partial applications where arguments are added without gaps.
Hence for a rule $r : A → B → C → D$, the applications $r~a~\_ : B \to D$ and $r~a~b : D$ for some $a : A$ and $b : B$ correspond to matches, but not $r~\_~b : A \to D$.
This prevents us from constructing $r~a~b$ in two different but ultimately redundant ways.
The term orders used in various saturation calculi have a similar effect.

@@

To account for this fact, we partition the set of premises of each rule into maximal subsets of premises connected by shared variables, called \emph{variable clusters}, using the same construction as Aesop's \emph{metavariable clusters}~\cite{Aesop}.
The variable clusters share no variables with each other, so each can be treated as a separate rule with its own rule state.
Finding a complete match for a rule then amounts to finding one complete match for each of its clusters.
The slots within each cluster can be ordered to ensure that each slot shares at least one variable with the previous slots.
